Baseline centering problem

### 2018-12-12 paper/tangotd.tex

Also, when observing a transition $s\to s'$, eligibility traces updates
the info about how to reach $s'$, while TD updates the info about the
reward when starting from $s$. I feel that somehow we have to use both:
intuitively when solving a problem we work ``from both ends'', expanding
both from the starting point and around the target.

>>>>

Also, when observing a transition $s\to s'$, eligibility traces update
the info about how to reach $s'$, while TD(0) updates the info about the
reward when starting from $s$. I feel that somehow we should use both:
intuitively when solving a problem we work ``from both ends'', expanding
both from the starting point and around the target.
